the rethinking way of doing the binary outcome modeling

### 2021-03-12 scripts/54_rethinking_binary.Rmd
do you know how hard is to make that plot

```{r}
library(rethinking)
library(tidyverse)  
```

@@

```{r}
# doing a prior check
prior <- extract.prior( mtox , n=1e4 ) 
# the diff in the probabilty of yes to toxicity when there are two std diff in diversity in each of the centers 
# for msk  
div_value <- c(-1, 1)
p <- sapply( 1:2 , function(k) inv_logit( prior$b * div_value[k] + prior$a[,1] ) )
mean( abs( p[,1] - p[,2] ) )
# the probability difference is pretty big !  # so reduced the std of the b from 1.5 to 0.25

# for upenn
p <- sapply( 1:2 , function(k) inv_logit( prior$b * div_value[k] + prior$a[,2] ) )
mean( abs( p[,1] - p[,2] ) )
```

@@

    ret = mean(abs( cols[[1]] -cols[[2]] ) )
    return(ret)

  })

@@

# don't know how to do the post check since the diversity is continuous variable

>>>>

```{r}
library(rethinking)
library(tidyverse) 
library(ggpubr)
```

@@

```{r}
# doing a prior check
prior <- extract.prior( mtox , n=1e4 ) 
# the diff in the probabilty of yes to toxicity when there are two std diff in diversity in each of the centers 
# for msk  
div_value <- c(-1, 1)

# make it into a function so that I can do the m and p the same time
prior_tox <- list(m = 1, p = 2) %>% 
  map(function(center_){
    cols = seq(1, length(div_value)) %>% 
      set_names(seq(1, length(div_value))) %>% 
      map(function(idx){
         inv_logit( prior$b * div_value[idx] + prior$a[, center_] ) 
      })

    diff = abs( cols[[1]] -cols[[2]] )
    ret = quantile(diff , probs = c(0.025, 0.5, 0.975))
    return(ret)
  }) 
```

@@

    diff = abs( cols[[1]] -cols[[2]] )
    ret = quantile(diff , probs = c(0.025, 0.5, 0.975))
    return(ret)
  }) 
```

```{r}
# visualize the prior and post together
tox <- bind_rows(
  bind_cols(prior_tox, grp ='prior', quant = c(0.025, 0.5, 0.975)),
  bind_cols(post_tox, grp ='post', quant = c(0.025, 0.5, 0.975))
)  %>% 
  gather('center', 'value', m:p) %>% 
  spread('quant', 'value') %>% 
  mutate(grp = factor(grp, levels = c('prior','post')))
tox
```
```{r}
tox %>% 
  ggscatter(x = 'center', y = '0.5', color = 'red', facet.by = 'grp', ylab = '', title = 'Difference in probability of responding yes when the diversity is 2 std apart') +
  geom_pointrange(aes( ymin  = `0.025`,ymax  = `0.975`), fatten = 5, col = 'red') +
  ylim(0,1) 
```

@@
